Supernovae Time Profiles as a Probe of New Physics at Neutrino Telescopes

### 2024-03-14 paper/main.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{\textit{Introduction}}---
The Standard Model (SM) is a remarkable but incomplete theory. 
Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the SM (BSM).
There are also no firmly established clues on the energy scale at which the new particles should appear.
To this end, numerous BSM searches across a wide range of scales have been performed, from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.

@@

The IceCube Neutrino Observatory has pioneered the detection of neutrinos at $\mathcal{O}$(PeV) energies~\cite{IceCube:2014stg,IceCube:2018cha} and has identified several specific astrophysical neutrino sources~\cite{IceCube:2018cha,IceCube:2023ame,IceCube:2022der}.
IceCube is also expected to be able to detect the next galactic SN~\cite{Kopke_2011}.
In fact, a search for MeV neutrinos from optically obscured galactic SNe was recently performed in \cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm}.
In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds. 
In this Letter, we will demonstrate that such precise time resolution will play a crucial role in testing new physics from SNe.

@@

We will set SN bounce time $t_{\rm bounce}$ as $t = 0$.
Using data from the simulation of $8.8 M_\odot$ progenitor star \cite{Huedepohl2010} and including effects of neutrino oscillations assuming normal mass ordering \cite{Dighe:1999bi}, we calculated standard neutrino fluxes at Earth. Following Ref.~\cite{Fiorillo:2022cdq}, we also calculated the flux of emitted Majorons.
At $t \leq \unit[0.05]{s}$, Majorons are mainly produced through $\nu_e$ and $\nu_x$ coalescence where $\nu_x$ includes (anti)neutrinos of $\tau$ and $\mu$ flavor. After $\unit[0.05]{s}$, the flux of Majorons decreases with the total flux of neutrinos of all flavors. Thus we found that the Majoron flux peaks around $t \sim \unit[0.05]{s}$. We further cross checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from SN energy loss.

\begin{figure}[t!]
\vspace{0.27cm}
    \centering
    \includegraphics[width=0.48\textwidth]{figures/Supernova_Diagram_Draft-2}
    \caption{\textbf{The decay geometry for Majorons produced in supernova.}}
    \label{fig:geometry}
\end{figure}

Very weakly coupled Majorons immediately stream out after being produced inside the star.
On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - m^2_\phi)/(2E_{\nu}E_\phi\beta)$. Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away (see the decay geometry in \cref{fig:geometry}).
The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a SN to reach the Earth is given by
\cite{Jaeckel:2017tud}
\begin{align}
    \delta t = \left(\frac{L_1}{\beta}-L_1\right) + (L_1 + L_2 -D_{\rm SN})\,,
    \label{eq:deltatexa}
\end{align}
where we have split the contribution to $\delta t$ into two parts: the first part comes from the slow-moving Majorons before their decay, and the second part is due to the detour from the line-of-sight path at the given emission angle $\alpha$.

@@

Since more than 93\% of the photons detected in IceCube originate in IBD interactions, the SM-only event rate peaks at around 0.1~s.
BSM scenarios, on the other hand, can give rise to an early or delayed signal depending on the particulars of the model.
In essence, Majorons can be generated before the peak of the SM $\bar{\nu}_{e}$ flux, and as light Majorons can travel nearly relativistically, they can escape the SNe with negligible time delay and then decay to an all-flavor flux of neutrinos, producing early $\bar{\nu}_{e}$ fluxes before the SM one.
The higher-mass Majorons, on the other hand, acquire a time delay from traveling sub-luminally and at a large detour, thus producing a later signal with sizable time delay.
We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different SN scenarios and the thermal and radioactive noise in the DOMs.
This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, IBD of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$. In addition to photons produced in neutrino interactions, it also simulates photons from thermal noise in the IceCube photomultipliers (PMTs) and from radioactive decay in the pressure glass housing.
In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY}~\cite{SNEWS:2021ewj} package and, in particular, the \texttt{ParametrizedFlux} object to parametrize the flux with the ``pinching'' factor~\cite{Keil:2002in,SNEWS:2021ewj}.

@@

With the number of hits in the detector from noise, SM-only scenarios, and BSM scenarios as a function of time, we can then quantify the probability of seeing a certain number of hits in a given time window with
\begin{equation}
    -2\Delta\mathrm{LLH} = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right],
    % -2\Delta\mathrm{LLH}(t_{\mathrm{start}}, \Delta t) = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right].
\end{equation}
where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis. For each BSM hypothesis, we then select the time range that maximizes the test statistic and use that maximal test statistic value. The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of the produced $\bar{\nu}_e$ flux.

In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the test statistic as a function of the time at which the time range begins, $t_{\mathrm{start}}$, and the duration of the time range, $\Delta t$, for an example BSM hypothesis. The distribution of test-statistic values is not sharply peaked in time, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$ \cite{Halzen_2009}.

@@

\textbf{\textit{Results and Discussions}}---
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_sensitivity}
    \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
    The lines on this plot show the exclusion sensitivity for IceCube, IceCube Gen-2, Hyper-Kamiokande and DUNE at $2\sigma$ CL.
    Additionally, we also show the reaches by SN cooling and by the lack of observation of high-energy neutrinos from SN1987A as black lines. 
    The sensitivities shown by the dashed line is obtained following~\cite{Brdar:2023tmi} with time-integrated data.
    }
    \label{fig:sensitivity}
\end{figure} 
Following our strategies above, we obtain the expected exclusion limits for various BSM scenarios from no observed excess of hits on top of background noise and standard neutrino flux.
The expected exclusion limits are presented in \cref{fig:sensitivity} for the Majoron case considering both IceCube and IceCube-Gen2. To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement, and non-observation of high-energy SN neutrinos from SN 1987A are also shown in \cref{fig:sensitivity} for the Majoron case. With future SN explosions, IceCube can improve current limits by one order of magnitude. 
Moreover, while current limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.

@@

\textit{Acknowledgements}---
We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching Ssupernovae simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/}) in machine-readable form, and also for stimulating discussions. Y.-Y. L is supported by the NSF of China through Grant No. 12305107, 12247103.
CAA are supported by the Faculty of Arts and Sciences of Harvard University, the National Science Foundation (NSF), the NSF AI Institute for Artificial Intelligence and Fundamental Interactions (IAIFI), the Research Corporation for Science Advancement, 
and the David \& Lucile Packard Foundation.
CAA and JL were partially supported by the Alfred P. Sloan Foundation for part of this work.
JL acknowledges support from the Belgian American Educational Foundation.

@@

\section{Appendix A: Dipole Magnetic Moment Portal}
\begin{figure}[hb!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/magnetic_moment_sensitivity}
    \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
    The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, and the limits computed in \cite{Brdar:2023tmi} for Hyper-Kamiokande and DUNE. 
    The sensitivities shown by the dashed line have been previously computed~\cite{Brdar:2023tmi} and use time-integrated data.
    %Sensitivities indicated by solid lines are newly computed in this work, whereas those shown by dashed lines have been previously computed in~\cite{Brdar:2023tmi}
    The shaded regions are excluded by the combination of energy loss requirement, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from SN explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
    }
    \label{fig:magnetic_moment_sensitivity}
\end{figure}
Here we also present results for active-to-sterile neutrino transition magnetic moment described by \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
\begin{align}
    \mathcal{L} \supset \sum_\alpha d_\alpha \bar{N}\sigma_{\mu\nu} \nu^{\alpha} F^{\mu\nu}-\frac{M_N}{2} \bar{N}^c N + \text{h.c.}\,,
    \label{eq:Lag}
\end{align}
where $\nu^{\alpha}$ and $N$ represent active and sterile neutrinos, respectively. Further, $F^{\mu\nu}$ is the field strength tensor of the electromagnetic field, $d_\alpha$ is the dimensionful coefficient of this dimension-5 term and $M_N$ is sterile neutrino mass.  We assume flavor universal interaction $d_\alpha \equiv d$. We consider the two production channels for $N$ inside the SN: $\nu e^- \to N e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies. Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}. The limits from IceCube are shown in SUPPL. \cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy SN explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}. We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from \cite{chauhan2024probing}. We notice that the time delay near the exclusion boundary is typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over the limits computed in \cite{Brdar:2023tmi} for DUNE and Hyper-Kamiokande.

>>>>

\textbf{\textit{Introduction}}---The Standard Model (SM) is a remarkable but incomplete theory. 
Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the SM (BSM).
Since there are also no firmly established clues on the energy scale at which the new particles should appear, numerous BSM searches across a wide range of scales have been performed: from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.

@@

\begin{figure}[t!]
\vspace{0.27cm}
    \centering
    \includegraphics[width=0.48\textwidth]{figures/Supernova_Diagram}
    \caption{\textit{\textbf{The decay geometry for Majorons produced in a SN.}}
    Both the additional distance travelled relative to the direct line of sight and the potential non-relativistic speed of the Majoran of can induce a delayed signal relative to the SM signal.
    }
    \label{fig:geometry}
\end{figure}

The IceCube Neutrino Observatory has pioneered the detection of neutrinos at $\mathcal{O}$(PeV) energies~\cite{IceCube:2014stg,IceCube:2018cha} and has identified several specific astrophysical neutrino sources~\cite{IceCube:2018cha,IceCube:2023ame,IceCube:2022der}.
IceCube is also expected to be able to detect the next galactic SN~\cite{Kopke_2011}.
In fact, a search for MeV neutrinos from optically obscured galactic SNe was recently performed in~\cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts~\cite{IceCube:2019acm}.
In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds. 
In this Letter, we will demonstrate that such precise time resolution will play a crucial role in testing new physics from SNe.

@@

We will set SN bounce time $t_{\rm bounce}$ as $t = 0$.
Using data from the simulation of $8.8 M_\odot$ progenitor star~\cite{Huedepohl2010} and including effects of neutrino oscillations assuming normal mass ordering~\cite{Dighe:1999bi}, we calculated standard neutrino fluxes at Earth. Following Ref.~\cite{Fiorillo:2022cdq}, we also calculated the flux of emitted Majorons.
At $t \leq \unit[0.05]{s}$, Majorons are mainly produced through $\nu_e$ and $\nu_x$ coalescence where $\nu_x$ includes (anti)neutrinos of $\tau$ and $\mu$ flavor. After $\unit[0.05]{s}$, the flux of Majorons decreases with the total flux of neutrinos of all flavors. Thus we found that the Majoron flux peaks around $t \sim \unit[0.05]{s}$. We further cross checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from SN energy loss.

Very weakly coupled Majorons immediately stream out after being produced inside the star.
On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - m^2_\phi)/(2E_{\nu}E_\phi\beta)$.
Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away;see the decay geometry in \cref{fig:geometry}.
The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a SN to reach the Earth is given by~\cite{Jaeckel:2017tud}
\begin{align}
    \delta t = \left(\frac{L_1}{\beta}-L_1\right) + (L_1 + L_2 -D_{\rm SN})\,,
    \label{eq:deltatexa}
\end{align}
where we have split the contribution to $\delta t$ into two parts: the first part comes from the slow-moving Majorons before their decay, and the second part is due to the detour from the line-of-sight path at the given emission angle $\alpha$.

@@

Since more than 93\% of the photons detected in IceCube originate in IBD interactions, the SM-only event rate peaks at around 0.1~s.
BSM scenarios, on the other hand, can give rise to an early or delayed signal depending on the particulars of the model.
In essence, Majorons can be generated before the peak of the SM $\bar{\nu}_{e}$ flux, and as light Majorons can travel nearly relativistically, they can escape the SNe with negligible time delay and then decay to an all-flavor flux of neutrinos, producing early $\bar{\nu}_{e}$ fluxes before the SM one.
The higher-mass Majorons, on the other hand, acquire a time delay from traveling sub-luminally and at a large detour, thus producing a later signal with sizable time delay.

We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different SN scenarios and the thermal and radioactive noise in the DOMs.
This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, IBD of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$. In addition to photons produced in neutrino interactions, it also simulates photons from thermal noise in the IceCube photomultipliers (PMTs) and from radioactive decay in the pressure glass housing.
In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY}~\cite{SNEWS:2021ewj} package and, in particular, the \texttt{ParametrizedFlux} object to parametrize the flux with the ``pinching'' factor~\cite{Keil:2002in,SNEWS:2021ewj}.

@@

With the number of hits in the detector from noise, SM-only scenarios, and BSM scenarios as a function of time, we can then quantify the probability of seeing a certain number of hits in a given time window with
\begin{equation}
\label{eq:likelihood}
    -2\Delta\mathrm{LLH} = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right],
    % -2\Delta\mathrm{LLH}(t_{\mathrm{start}}, \Delta t) = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right].
\end{equation}
where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis. 
For each BSM hypothesis, we select the time range that maximizes the test statistic and use that maximal test statistic value.
The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of the produced $\bar{\nu}_e$ flux.

In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the test statistic as a function of the time at which the time range begins, $t_{\mathrm{start}}$, and the duration of the time range, $\Delta t$, for an example BSM hypothesis. The distribution of test-statistic values is not sharply peaked in time, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$~\cite{Halzen_2009}.

@@

\textbf{\textit{Results and Discussions}}---
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_sensitivity}
    \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
    The lines on this plot show the exclusion sensitivity for IceCube, IceCube Gen-2, Hyper-Kamiokande and DUNE at $2\sigma$ CL.
    Additionally, we also show the reaches by SN cooling and by the lack of observation of high-energy neutrinos from SN1987A as black lines. 
    The sensitivities shown by the dashed line is obtained following~\cite{Brdar:2023tmi} with time-integrated data.
    }
    \label{fig:sensitivity}
\end{figure} 
Under the assumption that no excess neutrino were seen above the expected detector backgrounds and SM neutrinos, we obtain the expected $2\sigma$ exclusion limits by finding the coupling where Eq.~\ref{eq:likelihood} is equal to 3.841.
These limits are presented in \cref{fig:sensitivity} for the Majoron case considering both IceCube and IceCube-Gen2.
To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
Current limits~\cite{Fiorillo:2022cdq} from the energy loss requirement, and non-observation of high-energy SN neutrinos from SN 1987A are also shown in \cref{fig:sensitivity} for the Majoron case.
A future SN explosions would enable IceCube to improve current limits by one order of magnitude. 
Moreover, while current limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.

@@

\textit{Acknowledgements}---
We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching supernovae simulations---available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/} in machine-readable form---and also for stimulating discussions.
We would also like to thank Jackapan Pairin for their help designing figures in this work.
Y.-Y. L is supported by the NSF of China through Grant No. 12305107, 12247103.
CAA are supported by the Faculty of Arts and Sciences of Harvard University, the National Science Foundation (NSF), the NSF AI Institute for Artificial Intelligence and Fundamental Interactions (IAIFI), the Research Corporation for Science Advancement, 
and the David \& Lucile Packard Foundation.
CAA and JL were partially supported by the Alfred P. Sloan Foundation for part of this work.
JL is supported frbyom the Belgian American Educational Foundation.

@@

\section{Appendix A: Dipole Magnetic Moment Portal}
\begin{figure}[hb!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/magnetic_moment_sensitivity}
    \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
    The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, and the limits computed in~\cite{Brdar:2023tmi} for Hyper-Kamiokande and DUNE. 
    The sensitivities shown by the dashed line have been previously computed~\cite{Brdar:2023tmi} and use time-integrated data.
    %Sensitivities indicated by solid lines are newly computed in this work, whereas those shown by dashed lines have been previously computed in~\cite{Brdar:2023tmi}
    The shaded regions are excluded by the combination of energy loss requirement, non-observation of photon and neutrino signals from SN1987A studied in~\cite{Brdar:2023tmi} and by constraints on the energy release from SN explosion (SNIIP explosion)~\cite{PhysRevLett.128.221103, chauhan2024probing}.
    }
    \label{fig:magnetic_moment_sensitivity}
\end{figure}
Here we also present results for active-to-sterile neutrino transition magnetic moment described by~\cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
\begin{align}
    \mathcal{L} \supset \sum_\alpha d_\alpha \bar{N}\sigma_{\mu\nu} \nu^{\alpha} F^{\mu\nu}-\frac{M_N}{2} \bar{N}^c N + \text{h.c.}\,,
    \label{eq:Lag}
\end{align}
where $\nu^{\alpha}$ and $N$ represent active and sterile neutrinos, respectively. Further, $F^{\mu\nu}$ is the field strength tensor of the electromagnetic field, $d_\alpha$ is the dimensionful coefficient of this dimension-5 term and $M_N$ is sterile neutrino mass.  We assume flavor universal interaction $d_\alpha \equiv d$. We consider the two production channels for $N$ inside the SN: $\nu e^- \to N e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies. Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$~\cite{Plestid:2020vqf}. The limits from IceCube are shown in SUPPL. \cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A~\cite{Brdar:2023tmi}, and constraints on the energy release from low-energy SN explosions (SNIIP)~\cite{PhysRevLett.128.221103, chauhan2024probing}. We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from~\cite{chauhan2024probing}. We notice that the time delay near the exclusion boundary is typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over the limits computed in~\cite{Brdar:2023tmi} for DUNE and Hyper-Kamiokande.
